*flippant* --- An R package for the automated analysis of dithionite scramblase

### 2016-06-09 inst/manuscript/manuscript.rmd
Transition to usage of algorithm 2;

```{r setting_up_r, echo = FALSE}
library(flippant, quietly = TRUE)
library(grid, quietly = TRUE)
library(magrittr, quietly = TRUE)
library(microbenchmark, quietly = TRUE)
library(multipanelfigure, quietly = TRUE)
library(stringi, quietly = TRUE)
flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
  unlist(use.names = FALSE) %>%
  stri_split(regex = ",", omit_empty = TRUE) %>%
  unlist(use.names = FALSE) %>%
  stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
  stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
  tail(n=length(.) - 1) %>%
  sort() %>%
  ( function(x){
    paste0(
      c(
        "*",
        paste0(head(x, n = length(x) - 1), collapse = "*, *"),
        "* and *",
        tail(x, n = 1),
        "*"),
      collapse = "")} )

@@

```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details). In (B) data is separately plotted for independent experiments, while (C) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
x <- flippant:::read_scramblase_input_file(
  file.path(tmpDir,"inputTable.txt"))
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- add_panel(
  figure = figure1,
  top_panel = 1,
  bottom_panel = 3,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_traces(x, time_max_sec = 350) + theme_bw())
figure1 <- add_panel(
  figure = figure1,
  top_panel = 4,
  bottom_panel = 5,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- add_panel(
  figure = figure1,
  top_panel = 6,
  bottom_panel = 7,
  left_panel = 1,
  right_panel = 2,
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  split_by_experiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
grid.draw(figure1)
```

@@

```{r noeval_demonstrate_plot, eval = FALSE}
# Plot PPR plot (Figure 1B)
scramblase_assay_plot("inputTable.txt", generation_of_algorithm = 1) + xlim(0, 2)
```

@@

```{r noeval_demonstrate_plot2, eval = FALSE}
# Plot PPR plot (Figure 1C)
scramblase_assay_plot("inputTable.txt",
  generation_of_algorithm = 1,
  split_by_experiment = FALSE) + 
xlim(0, 2)
```

@@

```{r noeval_demonstrate_tabular_writeout, eval = FALSE}
# Write out results in tabular manner (Table 1)
scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 1, split_by_experiment = FALSE)
```

```{r analysis_tabular_output, echo = FALSE}
ppr_results <- scramblase_assay_stats(x, generation_of_algorithm = 1, split_by_experiment = FALSE)
ppr_results_names <- ppr_results$`Experimental Series` %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results$`Fit Constant` %>%
  signif(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of *flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
```

The resulting values for the fit constant $\alpha$ correspond with
`r ppr_results_alpha_print` for `r ppr_results_names`, respectively, very well
to the prior manual analysis by @ploier_perturbed_submitted, where
$\alpha \approx 0.13$ was reported for mutant and $\alpha \approx 0.26$ for wild
type rhodopsin. Based on the manual analysis of the data we conclude in @ploier_perturbed_submitted that the mutant rhodopsins investigated are
reconstituted into proteoliposomes in monomeric form, contrary to the wild type,
which is reconstituting as a homodimer. 
*flippant* analysis of the data shows identical trends and close matches of the
results, supporting identical conclusions.

@@

analysis_timing_function <- function(){
  scramblase_assay_traces(
    x,
    time_max_sec = 350)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1,
    split_by_experiment = FALSE)
  scramblase_assay_stats(
    x,
    generation_of_algorithm = 1, 
    split_by_experiment = FALSE)
}

>>>>

```{r setting_up_r, echo = FALSE}
library(dplyr)
library(flippant, quietly = TRUE)
library(grid, quietly = TRUE)
library(magrittr, quietly = TRUE)
library(microbenchmark, quietly = TRUE)
library(multipanelfigure, quietly = TRUE)
library(stringi, quietly = TRUE)
flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
  unlist(use.names = FALSE) %>%
  stri_split(regex = ",", omit_empty = TRUE) %>%
  unlist(use.names = FALSE) %>%
  stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
  stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
  tail(n=length(.) - 1) %>%
  sort() %>%
  ( function(x){
    paste0(
      c(
        "*",
        paste0(head(x, n = length(x) - 1), collapse = "*, *"),
        "* and *",
        tail(x, n = 1),
        "*"),
      collapse = "")} )

@@

```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details). In (B) data is separately plotted for independent experiments, while (C) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
x <- flippant:::read_scramblase_input_file(
  file.path(tmpDir,"inputTable.txt"))
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- add_panel(
  figure = figure1,
  top_panel = 1,
  bottom_panel = 3,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_traces(x, time_max_sec = 350) + theme_bw())
figure1 <- add_panel(
  figure = figure1,
  top_panel = 4,
  bottom_panel = 5,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_plot(x, generation_of_algorithm = 2) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- add_panel(
  figure = figure1,
  top_panel = 6,
  bottom_panel = 7,
  left_panel = 1,
  right_panel = 3,
  panel = scramblase_assay_plot(x, generation_of_algorithm = 2, split_by_experiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
grid.draw(figure1)
```

@@

```{r noeval_demonstrate_plot, eval = FALSE}
# Plot PPR plot (Figure 1B)
scramblase_assay_plot("inputTable.txt", generation_of_algorithm = 2) + xlim(0, 2)
```

@@

```{r noeval_demonstrate_plot2, eval = FALSE}
# Plot PPR plot (Figure 1C)
scramblase_assay_plot("inputTable.txt",
  generation_of_algorithm = 2,
  split_by_experiment = FALSE) + 
xlim(0, 2)
```

@@

```{r noeval_demonstrate_tabular_writeout, eval = FALSE}
# Write out results in tabular manner (Table 1)
scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 2, split_by_experiment = FALSE)
```

```{r analysis_tabular_output, echo = FALSE}
ppr_results <- scramblase_assay_stats(
    x, generation_of_algorithm = 2, split_by_experiment = FALSE) %>%
  mutate(`Fit Constant` = round(`Fit Constant` * 10E3, 2)) %>%
  set_names(c("Experimental Series", "Fit Constant ($\\times 10^3$)"))
ppr_results_names <- ppr_results %>%
  extract2("Experimental Series") %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results %>%
  extract2("Fit Constant ($\\times 10^3$)") %>%
  round(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant ($\\times 10^3$)`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of *flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
```

The resulting values for the fit constant $\alpha$ correspond with
`r ppr_results_alpha_print` for `r ppr_results_names`, respectively, well to the
prior manual analysis by @ploier_perturbed_submitted (Table S2), where $\alpha
\times 10^3 \approx 16$ was reported for mutant and $\alpha \times 10^3 \approx
7$ for wild type rhodopsin. Based on the manual analysis of the data we conclude
in @ploier_perturbed_submitted that the mutant rhodopsins investigated are
reconstituted into proteoliposomes in monomeric form, contrary to the wild type,
which is reconstituting as a homodimer. 
*flippant* analysis of the data shows identical trends and close matches of the
results, supporting identical conclusions.

@@

analysis_timing_function <- function(){
  scramblase_assay_traces(
    x,
    time_max_sec = 350)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 2)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 2,
    split_by_experiment = FALSE)
  scramblase_assay_stats(
    x,
    generation_of_algorithm = 2, 
    split_by_experiment = FALSE)
}
